The CMS Data Aggregation System

### 2010-05-04 doc/das_paper/paper.tex
Final tupe-up
git-svn-id: svn+ssh://svn.cern.ch/reps/CMSDMWM/DAS/trunk@995 4525493e-7705-40b1-a816-d608a930855b

%\author[vkuznet]{Valentin Kuznetsov\corref{cor1}}
\author[vkuznet]{Valentin Kuznetsov}
\address[vkuznet]{Cornell University, Ithaca, New York, USA}
%\ead{vkuznet@gmail.com}

\author[evans]{Dave Evans}
\address[evans]{Fermilab, Batavia, Illinois, USA}
%\ead{evansde@fnal.gov}

\author[metson]{Simon Metson}
\address[metson]{Bristol University, Bristol, UK}
%\ead{s.metson@bristol.ac.uk}

%\cortext[cor1]{Corresponding author}

@@

When a query for block meta-data is made, we are
%Upon a user request to 
%find a block meta-data, we were 
able to identify the appropriate set of 
DBS and PhEDEx APIs, retrieve the raw data from the services, format it
for DAS use and add the resulting information to the DAS cache. The records
are merged (aggregated) based on identical key-value pairs, e.g.
based on \verb+block.name+ key. Here is an example of such an aggregated record:
\begin{verbatim}
{"das_id": ["4b195404e2194e21c4000030", "4b1953fee2194e21c4000002"], 
 "block": [{"name": "/a/b/c#123", "replica": [{"complete": "y", 
            "subscribed": "n", "site": "T1_US_Buffer", "nfiles": "18", 
            "se": "a.b.com", "size": "112694171838"}, {....}]},
           {"name": "a/b/c#123", "nevents": "570200", 
            "created_by": "USER_DN", "path": "/a/b/c", ...}],
 "das": {"expire": 1259952908}}
\end{verbatim}
The \verb+das_id+ indicates the records stored in the DAS Analytics DB,
the \verb+block+ part represents the aggregated block meta-data information from DBS
and PhEDEx and the \verb+das+ part contains expiration time stamps
about how long the information is valid.
Usage of this information was a valuable contribution in debugging process of
data-services themselves, e.g. identification of data-service inconsistencies, 
latency studies, etc.

@@

\begin{table*}[hbt]
\centering
\begin{tabular}{lllll}\hline
\hline
System & Format & Records & Elapsed time & Elapsed time \\
& & & no cached data & w/ cached data \\
\hline
DBS yield & XML & 386943 & 68 sec & 0.98 sec \\
PhEDEx yield & XML & 189679 & 107 sec & 0.98 sec \\
Merge step & JSON & 576622 & 63 sec & 0.9 sec \\
DAS total & JSON & 392635 & 238 sec & 2.05/50.7 sec \\
\hline
\hline
\end{tabular}
\caption{Time required to fetch, parse and aggregate block information
from DBS and PhEDEx systems. The last row shows aggregated results and 
total time spent in all DAS components.
The total number of DAS records are calculated as the number of 
aggregated records plus left overs, the non-matched records from both systems. 
The look-up time shown in the last column represents the query look-up 
time (2.05 sec) and time required to get all records written 
to disk (50.7 sec).}
\label{DAS_benchmark}
\end{table*}

>>>>

\author[vkuznet]{Valentin Kuznetsov\corref{cor1}}
%\author[vkuznet]{Valentin Kuznetsov}
\address[vkuznet]{Cornell University, Ithaca, New York, USA}
\ead{vkuznet@gmail.com}
\author[evans]{Dave Evans}
\address[evans]{Fermilab, Batavia, Illinois, USA}
%\ead{evansde@fnal.gov}
\author[metson]{Simon Metson}
\address[metson]{Bristol University, Bristol, UK}
%\ead{s.metson@bristol.ac.uk}

\cortext[cor1]{Corresponding author}

@@

When a query for block meta-data is made, we are
%Upon a user request to 
%find a block meta-data, we were 
able to identify the appropriate set of 
DBS and PhEDEx APIs, retrieve the raw data from the services, format it
for DAS use and add the resulting information to the DAS cache. The records
are merged (aggregated) based on identical key-value pairs, e.g.
based on \verb+block.name+ key. Here is an example of such an aggregated record:
\begin{verbatim}
{"das_id": ["4b195404e2194e21c4000030", "4b1953fee2194e21c4000002"], 
 "block": [{"name": "/a/b/c#123", "replica": [{"complete": "y", 
            "site": "T1_US", "nfiles": "18", "se": "a.b.com"}, {...}]},
           {"name": "/a/b/c#123", "nevents": "570200", "path":"/a/b/c"}],
 "das": {"expire": 1259952908}}
\end{verbatim}
The \verb+das_id+ indicates the records stored in the DAS Analytics DB,
the \verb+block+ part represents the aggregated block meta-data information from DBS
and PhEDEx and the \verb+das+ part contains expiration time stamps
about how long the information is valid.
Usage of this information was a valuable contribution in debugging process of
data-services themselves, e.g. identification of data-service inconsistencies, 
latency studies, etc.

@@

\begin{table*}[hbt]
\centering
\begin{tabular}{lllll}\hline
\hline
System & Format & Records & Elapsed time & Elapsed time \\
& & & no cached data & w/ cached data \\
\hline
DBS yield & XML & 386943 & 68 sec & 0.98 sec \\
PhEDEx yield & XML & 189679 & 107 sec & 0.98 sec \\
Merge step & JSON & 576622 & 63 sec & 0.9 sec \\
DAS total & JSON & 392635 & 238 sec & 2.05/50.7 sec \\
\hline
\hline
\end{tabular}
\caption{Time required to fetch, parse and aggregate block information
from DBS and PhEDEx systems. The last row shows aggregated results and 
total time spent in all DAS components.
The total number of DAS records are calculated as the number of 
aggregated records plus left overs, the non-matched records from both systems. 
The look-up time shown in the last column represents the query look-up 
time (2.05s) and time required to get all records written 
to disk (50.7s).}
\label{DAS_benchmark}
\end{table*}
